---
title: "Censored outcomes"
---

```{r}
#| label: setup

# Packages
library(scales)
library(knitr)
library(here)
library(janitor)
library(latex2exp)
library(brms)
library(distributional)
library(posterior)
library(rstan)
library(patchwork)
library(tidybayes)
library(ggdist)
library(tidyverse)

# Some settings common to all modules
source(here("modules/_common.R"))
```

## Example data

Experiment 1 from @metcalfe2022:

> Procedure. Ninety general information questions (see theonline supplemental material) from Nelson and Narens’ (1980) norms, as updated in Bloom et al. (2018), were presented in a random order. The participant typed in an answer and then made a con dence judgment about the correctness of their answer on a sliding scale from 0% (not at all confident) to 100% (completely confident). They were then given yes/no feedback about the correctness of their answer. If incorrect, they rated their curiosity to find out the correct answer on a sliding scale from 0% (do not care) to 100% (care very much).

```{r}
dat <- read_rds(here("data/metcalfe.rds"))

dat <- dat |> 
  mutate(
    confidence = confidence / 100,
    curiosity = curiosity / 100
  )

head(dat) |> 
  kable()
```

```{r}
dat <- dat |> 
  mutate(
    cl_confidence = case_when(
      confidence == 0 ~ "left",
      confidence == 1 ~ "right",
      TRUE ~ "none"
    ),
    cl_curiosity = case_when(
      curiosity == 0 ~ "left",
      curiosity == 1 ~ "right",
      TRUE ~ "none"
    )
  )

head(dat) |> 
  kable()
```

```{r}
pa <- dat |> 
  ggplot(aes(confidence, fill = accuracy)) +
  scale_fill_brewer(
    "Accuracy",
    palette = "Set1"
  ) +
  geom_histogram(position = "dodge")

pb <- pa %+% 
  filter(
    pa$data, 
    subject %in% sample(unique(dat$subject), 9)
  ) +
  facet_wrap("subject")

(pa | pb) + 
  plot_layout(guides = "collect", axis_titles = "collect")
```

## Models

```{r}
bf_g <- bf(
  confidence ~
    1 + accuracy +
    (1 + accuracy | subject) 
) +
  gaussian()

fitg <- brm(
  bf_g,
  data = dat,
  control = list(adapt_delta = .95),
  file = here("models/censored-0")
)
```

```{r}
bf_c <- bf(
  confidence | cens(cl_confidence) ~
    1 + accuracy +
    (1 + accuracy | subject) 
) +
  gaussian()

fitc <- brm(
  bf_c,
  data = dat,
  control = list(adapt_delta = .95),
  file = here("models/censored-1")
)
```

## Summary

```{r}
summary(fitg)
summary(fitc)
```

## Model comparison

```{r}
#| echo: true
#| results: hide

# Add LOO criteria to all models
fitg <- add_criterion(fitg, "loo")
fitc <- add_criterion(fitc, "loo")
```

```{r}
loo_compare(
  fitc, fitg
)
```

- What is happening?
